---
title: "Welcome90 Merging and"
author: "Joshua Scriven"
date: Sys.Date()
output: html_notebook
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message=FALSE)
```

```{r custom_functions, include=FALSE}
source("https://raw.githubusercontent.com/joshuascriven/helper_functions/main/helper_functions.R")
```

```{r, include=FALSE}
# devtools::install_github('Mikata-Project/ggthemr')
packageloader(c("openxlsx", "readxl", "tidyverse", "dplyr", "knitr", "stargazer", "gtsummary", "english", "scales", "ggpubr", "broom", "AICcmodavg", "lmtest", "sandwich", "reshape2","qualtRics","odbc","lubridate","stringr","Hmisc","anytime","wesanderson","wordcloud","wordcloud2","RColorBrewer","tm","fastDummies","jtools","ggcorrplot","pampe","plm","stringdist","rgeolocate","DBI","rstudioapi","ggthemr","janitor","ggpubr","stackoverflow","fuzzyjoin","gtools"))

```

```{r data, warning=FALSE, cache=TRUE, include=FALSE}
ggthemr("flat")

# set data dir and project name
data_dir <- "../data/"
projname <- "qo_request_JS7"
api_key <- read.table(filemaker("api_key","txt"))

outpath <- paste0(here() %>% str_remove(projname),"qo_requests_admin/out/",projname)
ifelse(!dir.exists(file.path(outpath)), dir.create(file.path(outpath), recursive = TRUE), "Already exists")
# 
# imgpath <- paste0(dirname(getSourceEditorContext()$path),"/figures")
# ifelse(!dir.exists(file.path(imgpath)), dir.create(file.path(imgpath), recursive = TRUE), "Already exists")

# main data file name
# files <- c("New hire update May June July",
#           "Rawdataexcel_orientation_26_08pull",
#           "Rawdataexcel_2021-08-18_smartsheets")
```

# Survey History

As of 29 June, 2022, W90 surveys have been conducted in some form on the following dates: 

- August 18, 2021
- September 22, 2021
- October 20, 2021

The single survey was split into distinct parts for these dates:

- February 16, 2022
- April 20, 2022

The distinct surveys remain as such, but are presented in Qualtris in a single location:

- June 20th, 2022

## Merging
Versions of the W90 surveys can be found on Formsite, Smartsheet, and Qualtrics. These must be merged.


```{r data, warning=FALSE, cache=TRUE, include=FALSE}
con <- dbConnect(odbc::odbc()
                 , driver="Smartsheet Live Data Connector"
                 , database="smartsheets"
                 , uid=api_key[4,]
                 , pwd=api_key[5,]
                 , timeout = 10)

survey_tables <- dbListTables(con)[str_detect (pattern = "^Archived_W90" , string =  dbListTables(con))]

surveys_names <- c(
  # "Archived_W90 Rawdataexcel_2021-08-18__4665147349329796s_"
  "Formsite_2021_08_18"
  # ,"Archived_W90 Rawdataexcel_2021-09-22__6372001712498564s_"
  ,"Formsite_2021_09_22"
  # ,"Archived_W90 Rawdataexcel_2021-10-26__6864995238602628s_"
  ,"Formsite_2021_10_26"
  # ,"Archived_W90 Survey - Day 1__6508768839133060s_"
  ,"Day_1"
  # ,"Archived_W90 Survey - Day 30__5489883679614852s_"
  ,"Day_30"
  # ,"Archived_W90 Survey - Day 90__5929568071640964s_"
  ,"Day_90"
  # ,"Archived_W90 Survey - Recruitment & Hiring__1161467178313604s_"
  ,"Rec_Hire"
  # ,"Archived_W90 Survey - WW Event__3594660640778116s_"
  ,"Event_Eval"
)

surveys <- list()
codebooks <- list()

for (s in seq_along(survey_tables)){
  surveys[[surveys_names[s]]] <-  dbGetQuery(con,  sprintf("SELECT * FROM [%s]",survey_tables[s]))
}

for (s in seq_along(survey_tables)){
  codebooks[[surveys_names[s]]] <-  scrivbook(data=surveys[[s]], mode="make:r", info_cols=c(
    "XQID"
    # ,"phase"
    # ,"longitudinal"
    ))
}


s <- dbListTables(con)[str_detect (pattern = "W90 Surveys Codebook_questions" , string =  dbListTables(con))]
survey_questions <-  dbGetQuery(con,  sprintf("SELECT * FROM [%s]",s)) %>% 
  rename(name_old=col_name)

questions <- list()

for (q in getunique(survey_questions$phase)){
  questions[[q]] <-  survey_questions %>% filter(phase==q)
}

surv_names <- mixedsort(names(surveys))
surv_types <- split(x = surv_names, f = grepl("Form",surv_names))
surv_texts <- mixedsort(names(questions))

for (s in seq_along(surv_types[[1]])){
  print(s)
  temp <- stringdist_join(codebooks[[ surv_types[[1]][s] ]], questions[[ surv_texts[s] ]], 
                                 by='name_old', #match based on team
                                 mode='left', #use left join
                                 method = "jw", #use jw distance metric
                                 max_dist=1, 
                                 distance_col='dist') %>%
    group_by(name_old.x) %>%
    slice_min(order_by=dist, n=1)
  
  codebooks[[ surv_types[[1]][s] ]] <- temp %>% 
    mutate(description=question_text) %>% 
    select(
      qid
      , name_old.x
      , description
      , name_new
      , display_names
      , display_names_short
      , comments
      , XQID
      # , col_name
      , phase
      , longitudinal
      # , question_text
      , open_end
    ) %>% 
    rename(name_old=name_old.x)
  
    # codebooks[[ surv_types[[1]][s] ]]
}

cols_add <- setdiff(names(codebooks[[ surv_types[[1]][1] ]]),names(codebooks[[ surv_types[[2]][1] ]]))

for (s in seq_along(surv_types[[2]])){
  print(s)
  temp <- codebooks[[ surv_types[[2]][s] ]]
  temp[cols_add] <- NA
  codebooks[[ surv_types[[2]][s] ]] <- temp %>%
    mutate(phase=surv_types[[2]][s]
           , description=name_old)
  
  # ["phase"] <- surv_types[[2]][s]
}

codebooks[["all_surveys"]] <- bind_rows(codebooks)
codebooks[["all_surveys"]]["XQNUM"] <- 1:nrow(codebooks[["all_surveys"]])
codebooks <- codebooks[c("all_surveys", surv_types[[1]], surv_types[[2]])]

outfile <- paste0(outpath,"/archived_survey_questions.xlsx")
write.xlsx(x = codebooks, file = outfile)
browseURL(outfile)


```
